---
title: "Module 6"
subtitle: "{{< var md-06.title >}}"
editor: source
params:
    week: 6
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

# Read variables and format dates
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-06`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-06`$`homework-due`), "%B %d, %Y")
quiz_due_date <- format(as.Date(vars$`md-06`$`quiz-due`), "%B %d, %Y")

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-06-vectors.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/content/slides/lec-06-vectors.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-06-vectors.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```


## {{< fa book >}} Readings

1. Read [R for Data Science - Section 7 - Data import](https://r4ds.hadley.nz/data-import)  
2. Read [R for Data Science - Section 10 - Exploratory data analysis](https://r4ds.hadley.nz/eda)  

## {{< fa code >}} Assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

-   [Assignment 1](../assignments/md-06/am-06-1-reading.qmd): Good enough practices in scientific computing
-   If you haven't yet, then: [Assignment 2](../assignments/md-05/am-05-1-project-data.qmd): Identify data for your capstone project

Thank you for working through this assignment.

## {{< fa clipboard-question >}} Quiz

[Due date:]{.highlight-yellow} `r quiz_due_date`

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.

[Quiz in preparation]{.highlight-yellow}

## {{< fa video >}} Session Recording

You can access the Zoom recording of Module 6 on `r session_date`. To watch the recording, you will need to register for it. 

Register for the recording at this link: [provided after the session]{.highlight-yellow} 

**Note: The video link will be shared once the recording is available.**