---
title: "Module 6"
subtitle: "{{< var md-06.title >}}"
editor: source
params:
    week: 8
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

# Read variables and format dates
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-06`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-06`$`homework-due`), "%B %d, %Y")
quiz_due_date <- format(as.Date(vars$`md-06`$`quiz-due`), "%B %d, %Y")

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-06-vectors.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/content/slides/lec-06-vectors.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-06-vectors.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```


## {{< fa book >}} Readings

1. Read [R for Data Science - Chapter 20 - Vectors](https://r4ds.hadley.nz/vectors)
2. Read [R for Data Science - Chapter 26 - Iteration](https://r4ds.hadley.nz/iteration)
3. Read [R for Data Science - Chapter 27 - A field guide to base R](https://r4ds.hadley.nz/base-r)  

## {{< fa code >}} Assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

-   [Assignment 1](../assignments/md-06/am-06-1-cross-references.qmd): Cross-references with Quarto (includes optional bonus on for-loops)
-   [Assignment 2](../assignments/md-06/am-06-2-reading.qmd): Good enough practices in scientific computing
-   If you haven't yet, then: [Assignment 3](../assignments/md-05/am-05-1-project-data.qmd): Identify data for your capstone project

::: {.callout-note}
## About Assignment 1

Assignment 1 includes a required section on cross-references and an optional bonus section on for-loops for those who want to deepen their understanding of iteration in R.
:::

Thank you for working through these assignments.

## {{< fa clipboard-question >}} Quiz

[Due date:]{.highlight-yellow} `r quiz_due_date`

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.

Access the quiz here: <https://u4x6xe-lars-sch0bitz.shinyapps.io/md-06-quiz/> [Note: The quiz will be available once it has been deployed.]{.highlight-yellow}

You can verify your submissions using our [Live Quiz Checker](../course/quiz-checker.qmd).

## {{< fa video >}} Session Recording

You can access the Zoom recording of Module 6 on `r session_date`. To watch the recording, you will need to register for it. 

Register for the recording at this link: <https://ethz.zoom.us/rec/share/cr-NCsCxzdYGWxExusXWmChBua941_dwEoz7Xs5qU-0ygvXsHlqdfIzyPg9yC3C0.jqJOJY8ja6i_WyYI> 

[Note: The video will show once the recording has been processed.]{.highlight-yellow}


