---
title: "Module 9"
subtitle: "{{< var md-09.title >}}"
editor: source
params:
    week: 12
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

# Read variables and format dates
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-09`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-09`$`homework-due`), "%B %d, %Y")
quiz_due_date <- format(as.Date(vars$`md-09`$`quiz-due`), "%B %d, %Y")

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```


## {{< fa display >}} Slides

- In preparation

## {{< fa code >}} Assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

- No assignments
- You can work on your [capstone project report](../project/)

## {{< fa clipboard-question >}} Quiz

[Due date:]{.highlight-yellow} `r quiz_due_date`

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.

[Quiz in preparation]{.highlight-yellow}

## {{< fa video >}} Session Recording

You can access the Zoom recording of Module 9 on `r session_date`. To watch the recording, you will need to register for it. 

Register for the recording at this link: [provided after the session]{.highlight-yellow} 

**Note: The video link will be shared once the recording is available.**
