---
title: "Module 3"
subtitle: "{{< var md-03.title >}}"
editor: source
params:
    week: 3
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

# Read variables and format dates
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-03`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-03`$`homework-due`), "%B %d, %Y")
quiz_due_date <- format(as.Date(vars$`md-03`$`quiz-due`), "%B %d, %Y")

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-03-transformation.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/content/slides/lec-03-transformation.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-03-transformation.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

1. Read [R for Data Science - Section 3 - Data transformation](https://r4ds.hadley.nz/data-transform)  

## {{< fa code >}} Assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

-   [Assignment 1](../assignments/md-03/am-03-1-data-transformation.qmd): Data transformation
-   [Assignment 2](../assignments/md-03/am-03-2-spreadsheet.qmd): Create a spreadsheet

Thank you for working through this assignment.

## {{< fa clipboard-question >}} Quiz

[Due date:]{.highlight-yellow} `r quiz_due_date`

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.

Access the quiz here: <https://u4x6xe-lars-sch0bitz.shinyapps.io/ds4owd-002-quiz/>

You can verify your submissions using our [Live Quiz Checker](../course/quiz-checker.qmd).

## {{< fa video >}} Session Recording

You can access the Zoom recording of Module 3 on `r session_date`. To watch the recording, you will need to register for it. 

Register for the recording at this link: <https://ethz.zoom.us/rec/share/OqFP-AjAHoFLU3K_dXpGg3WKY0ZduktHQ_1sMDaCsSrmUPmu1QyH2upvadeGOBWc.JWrsSNEI4C6lpb9L>

[Note: The video will show once the recording has been processed.]{.highlight-yellow}



**Note: The video link will be shared once the recording is available.**
