---
title: "Module 2"
subtitle: "{{< var md-02.title >}}"
editor: source
params:
    week: 2
execute: 
  echo: false
  warning: false
bibliography: ../../ds4owd-002.bib
---

Are you ready for some data visualisations? This week is all about exploring data with `ggplot2` R package. We will also learn about the data science lifecycle. 

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

# Read variables and format dates
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-02`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-02`$`homework-due`), "%B %d, %Y")
quiz_due_date <- format(as.Date(vars$`md-02`$`quiz-due`), "%B %d, %Y")

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-02-visualisation.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/content/slides/lec-02-visualisation.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-02-visualisation.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```


## {{< fa book >}} Readings

1. Read [R for Data Science - Whole game](https://r4ds.hadley.nz/whole-game)
2. Read [R for Data Science - Section 3 - Workflow basics](https://r4ds.hadley.nz/workflow-basics) 
3. Read [R for Data Science - Section 2 - Data visualization](https://r4ds.hadley.nz/data-visualize)

## {{< fa code >}} Assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

Please complete the following assignments before the due date.

-   [Assignment 1](../assignments/md-02/am-02-1-bookmarks.qmd): Support yourself with bookmarks
-   [Assignment 2](../assignments/md-02/am-02-2-data-visualisation.qmd): Data visualisation

Thank you for working through these assignments.

## {{< fa clipboard-question >}} Quiz

[Due date:]{.highlight-yellow} `r quiz_due_date`

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.

Access the quiz here: <https://u4x6xe-lars-sch0bitz.shinyapps.io/ds4owd-002-quiz/>

You can verify your submissions using our [Live Quiz Checker](../course/quiz-checker.qmd).

## {{< fa video >}} Session Recording

You can access the Zoom recording of Module 2 on `r session_date`. To watch the recording, you will need to register for it. 

Register for the recording at this link: <https://ethz.zoom.us/rec/share/fxfezDds1UPpXjY-47ZIZN0be1nf9WFkt5wbm4zjf0CsVJEt9wyketdOKfleo-E_.GKy6wztwALoYMyjj>

[Note: The video will show once the recording has been processed.]{.highlight-yellow}


