---
title: "Module 10"
subtitle: "{{< var md-10.title >}}"
editor: source
execute:
  echo: false
  warning: false
---

## {{< fa graduation-cap >}} Graduation Event

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: event-info

# Read variables and format date
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-10`$date), "%B %d, %Y")
```

Congratulations on completing the ds4owd-002 course! Join us for our graduation celebration on `r session_date`.

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-10-graduation.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/content/slides/lec-10-graduation.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-10-graduation.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa calendar >}} Event Agenda

```{r}
agenda <- readr::read_csv(here::here("data/tbl-04-ds4owd-002-graduation.csv"))

agenda |>
    dplyr::mutate(
      time = format(start_time, "%H:%M"),
      # Create hyperlinked title if project_link exists
      title = ifelse(
        !is.na(project_link),
        paste0("[", title, "](", project_link, ")"),
        title
      )
    ) |>
    dplyr::select(time, duration, title, speaker) |>
    dplyr::mutate(
      duration = format(duration, "%M min"),
      speaker = ifelse(is.na(speaker), "", speaker)
    ) |>
    dplyr::rename_with(~stringr::str_to_title(.x), everything()) |>
    knitr::kable()
```

## {{< fa trophy >}} Course Completion

You successfully complete the course and receive a certificate of completion if you:

1. [Hand in a complete capstone project report]{.highlight-yellow} that uses a dataset of your choice
2. Complete all quizzes from module 1 through module 6

## {{< fa clipboard-check >}} Post-Course Survey

We would appreciate your feedback! Please complete the short post-course survey:

<https://forms.gle/cahqbLBoGt4eKu7K8>

Without the free-text questions, the survey will take a maximum of 5 minutes to complete.

## {{< fa newspaper >}} Stay Connected

Subscribe to the [openwashdata newsletter](https://buttondown.com/openwashdata) to receive:

- Updates on future workshops
- Insights into data collected during the course
- News about the openwashdata community

## {{< fa video >}} Session Recording

We will not record this session.
