---
title: "Module 1"
subtitle: "{{< var md-01.title >}}"
editor: source
params:
    week: 1
execute: 
  echo: false
  warning: false
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

This first week will be used to get you set up for the course. 

## Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

# Read variables and format dates
vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-01`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-01`$`homework-due`), "%B %d, %Y")
quiz_due_date <- format(as.Date(vars$`md-01`$`quiz-due`), "%B %d, %Y")

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-01-welcome.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/slides/lec-01-welcome.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-01
-welcome.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

- Read the [Course Overview](../index.html).

## {{< fa code >}} Assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

Please complete the following assignments before the due date. They are a pre-requisite for the second module.

-   [Assignment 1](../assignments/md-01/am-01-1-posit.qmd): In class: Working with R, RStudio on Posit Cloud
-   [Assignment 2](../assignments/md-01/am-01-2-element.qmd): Homework: Communication in a chat
-   [Assignment 3](../assignments/md-01/am-01-3-github-pat.qmd): Homework: GitHub Personal Access Token 
-   [Assignment 4](../assignments/md-01/am-01-4-github-clone.qmd): Homework: Clone a GitHub repository 
-   [Assignment 5](../assignments/md-01/am-01-5-github-workflow.qmd): Homework: GitHub workflow

Thank you for working through these assignments.

## {{< fa clipboard-question >}} Quiz

[Due date:]{.highlight-yellow} `r quiz_due_date`

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.

[Quiz in preparation]{.highlight-yellow}

## {{< fa video >}} Session Recording

You can access the Zoom recording of Module 1 on `r session_date`. To watch the recording, you will need to register for it. 

Register for the recording at this link: [provided after the session]{.highlight-yellow} 

**Note: The video link will be shared once the recording is available.**