---
title: "Module 8"
subtitle: "{{< var md-08.title >}}"
editor: source
params:
    week: 12
execute: 
  echo: false
  warning: false
---

## {{< fa bullseye >}} Learning Objectives

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-08-quarto.html) | [Download slides as PDF](https://github.com/ds4owd-002/website/raw/main/slides/lec-08-quarto.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-08-quarto.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

1. Read [R for Data Science - Section 28 - Quarto](https://r4ds.hadley.nz/quarto)

## {{< fa code >}} Assignments

**Due date:** Wednesday, {{< var md-08.homework-due >}}

- No assignments
- You can work on your [capstone project report](../project/)

## {{< fa clipboard-question >}} Quiz

**Due date:** Wednesday, {{< var md-08.quiz-due >}}

Complete this quiz after you have worked through the assignments. Completing the quiz of each week is required to receive a course certificate at the end of the course.
