---
title: "{{< var md-09.title >}}"
subtitle: "{{< var course.long-title >}}"
author: "{{< var author >}}"
date-format: "MMM D, YYYY"
date: "2025-11-27"
format:
  revealjs:
    theme: slides.scss
    transition: fade
    slide-number: true
    logo: ../../img/OWD-logo-20.png
    chalkboard: true
footer: "[{{< fa link >}} {{< var course.site-short >}}]({{< var course.site >}})"
editor: source
execute:
  freeze: auto
params:
    week: 12
bibliography: references.bib
csl: apa.csl
editor_options:
  chunk_output_type: console
---


```{r}
library(countdown)
```

# Five Approaches

## Five Approaches to AI Assistance

::: {.incremental}
1. **Chatbots** - Conversational code generation (e.g., duck.ai, ChatGPT)
2. **Code Completion** - Real-time suggestions (e.g., GitHub Copilot)
3. **In-IDE Chat** - Context-aware assistance within your IDE
4. **Agentic Tools** - Autonomous coding assistance (e.g., Claude Code)
5. **R Packages** - Programmatic AI integration (e.g., ellmer)
:::

::: .notes

1. Chatbots: here is the problem, write R code for that

2. Inline autocomplete: modern IDEs bring in autocomplete, one of the skills of programming today is to ignore it when it's bad and accept it when it's good

3. In-IDE chat: that's mostly for convenience and is like chatting with a Chat provider like duck.ai, the chat knows more about what you are doing because it can see what you are working on

4. Agentic coding: newest trend, Cursor, Claude Code, LLM goes off and writes a bunch of code

5. R Packages: programmatic access to AI capabilities, ellmer, gptstudio, openai, anthropic
::: 

# Approach 1: Chatbot Assistance {background-color="#4C326A"}

## What are AI Chatbots?

Conversational interfaces that:

- Understand natural language questions
- Generate code based on descriptions
- Explain existing code
- Debug and suggest improvements
- Iterate based on your feedback

. . .

**Examples:** ChatGPT, Claude, duck.ai, Perplexity

## duck.ai Overview

::: columns
::: {.column width="50%"}
**Features**

- Free and privacy-focused
- Multiple AI models
- Code-aware responses
- No account required
- Built by DuckDuckGo
:::

::: {.column width="50%"}
**Best for**

- Quick code generation
- Learning new functions
- Understanding errors
- Exploring approaches
- Documentation assistance
:::
:::

## {{< fa person-chalkboard >}} My Turn: duck.ai Demo {.center-align}

::: {.hand-purple-large style="text-align: center;"}
Sit back and enjoy!
:::

::: {style="margin-top: 30px"}
I'll demonstrate:

1. Describing the task clearly
2. Providing context about the data
3. Reviewing generated code
4. Iterating to improve the solution
5. Testing the code in RStudio
:::

```{r}
countdown(10)
```

## Example: Good Prompt for EDA

::: {.callout-tip icon=false}
## Your Turn: Try this prompt

I have a CSV dataset available at this GitHub raw link: [PASTE URL HERE]

Please help me perform exploratory data analysis using R tidyverse packages. Specifically:

1. Load the data and display its structure
2. Summarize key variables (numeric and categorical)
3. Check for missing values
4. Create visualizations to understand distributions and relationships
5. Identify any unusual patterns or potential data quality issues

Please provide well-commented R code using tidyverse packages (dplyr, ggplot2, etc.) that I can run in RStudio.
:::

# Approach 2: Code Completion {background-color="#4C326A"}

# Approach 3: In-IDE Chat {background-color="#4C326A"}

# Approach 4: Agentic Tools {background-color="#4C326A"}

# Approach 5: R Packages {background-color="#4C326A"}
 

## Clear win: translations

- Pseudo code -> code
- Latex -> Quarto
- SQL -> dplyr
- SAS / STATA / SPSS -> R
- Words -> regular expressions
- Image to shiny app / Quarto dashboard

::: {.notes}
Keynote: I Wrote This Talk with an LLM - Hadley Wickham
:::

## LLM concerns

- **Cost/equality of access**: $5 on Claude gets you pretty far; Gemini has a generous free tier. Local models not worth it IMO (but maybe gpt-oss changes that).

- **Environmental concerns**: worth considering, but small and decreasing on individual level. More impactful ways to save energy/water.

- **Data privacy**: legit as individual. Not a problem for most bigger orgs as most data already lives in some cloud, and cloud providers run LLMs.

::: {.notes}
Keynote: I Wrote This Talk with an LLM - Hadley Wickham
:::
