---
title: "{{< var md-09.title >}}"
subtitle: "{{< var course.long-title >}}"
author: "{{< var author >}}"
date-format: "MMM D, YYYY"
date: "2025-11-27"
format:
  revealjs:
    theme: slides.scss
    transition: fade
    slide-number: true
    logo: ../../img/OWD-logo-20.png
    chalkboard: true
footer: "[{{< fa link >}} {{< var course.site-short >}}]({{< var course.site >}})"
editor: source
execute:
  freeze: auto
params:
    week: 12
bibliography: references.bib
csl: apa.csl
editor_options:
  chunk_output_type: console
---

```{r}
#| include: false
library(countdown)
library(epoxy)
```

## Learning Objectives

```{r}
#| label: learning-objectives
#| echo: false
lobj <- readr::read_csv(here::here("data/tbl-02-ds4owd-002-learning-objectives.csv")) |>
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)
```

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

# The AI Revolution in Software Development {background-color="#4C326A"}

## Why AI for R Development?

::: columns
::: {.column width="50%"}
**Traditional Workflow**

- Search Stack Overflow
- Read documentation
- Trial and error
- Debug manually
- Write boilerplate code
:::

::: {.column width="50%"}
**AI-Enhanced Workflow**

- Ask AI conversationally
- Get code suggestions in real-time
- Automate repetitive tasks
- Intelligent debugging
- Generate code from descriptions
:::
:::

## Four Approaches to AI Assistance

::: {.incremental}
1. **Chatbots** - Conversational code generation (e.g., duck.ai, ChatGPT)
2. **Code Completion** - Real-time suggestions (e.g., GitHub Copilot)
3. **Agentic Tools** - Autonomous coding assistance (e.g., Claude Code)
4. **R Packages** - Programmatic AI integration (e.g., ellmer, gptstudio)
:::

## Today's Agenda

- **10 min** - Chatbot approach (My Turn: duck.ai demo)
- **15 min** - Chatbot approach (Your Turn: WASH data task)
- **5 min** - GitHub Copilot overview
- **10 min** - Agentic work mode (My Turn: Claude Code demo)
- **15 min** - R packages (My Turn: ellmer for PDF extraction)
- **5 min** - Resources and best practices

# Approach 1: Chatbot Assistance {background-color="#4C326A"}

## What are AI Chatbots?

Conversational interfaces that:

- Understand natural language questions
- Generate code based on descriptions
- Explain existing code
- Debug and suggest improvements
- Iterate based on your feedback

. . .

**Examples:** ChatGPT, Claude, duck.ai, Perplexity

## duck.ai Overview

::: columns
::: {.column width="50%"}
**Features**

- Free and privacy-focused
- Multiple AI models
- Code-aware responses
- No account required
- Built by DuckDuckGo
:::

::: {.column width="50%"}
**Best for**

- Quick code generation
- Learning new functions
- Understanding errors
- Exploring approaches
- Documentation assistance
:::
:::

## {{< fa person-chalkboard >}} My Turn: duck.ai Demo {.center-align}

**Task:** Transform and visualize WASH data

::: {style="margin-top: 30px"}
I'll demonstrate:

1. Describing the task clearly
2. Providing context about the data
3. Reviewing generated code
4. Iterating to improve the solution
5. Testing the code in RStudio
:::

```{r}
#| echo: false
countdown(minutes = 10, seconds = 0)
```

## Tips for Effective Chatbot Prompts

::: {.incremental}
1. **Be specific** - "Create a ggplot2 bar chart" vs "Make a chart"
2. **Provide context** - Share data structure, column names, goal
3. **Iterate** - Start simple, then refine
4. **Review carefully** - AI can make mistakes
5. **Ask for explanations** - Understand the code, don't just copy
:::

## {{< fa users >}} Your Turn: Chatbot Exercise {.center-align}

::: {style="margin-top: 30px"}
**Time:** 15 minutes

**Task:** Use duck.ai to solve a WASH data problem

See the exercise instructions in your repository:
`md-10-exercises`
:::

```{r}
#| echo: false
countdown(minutes = 15, seconds = 0)
```

# Approach 2: GitHub Copilot {background-color="#4C326A"}

## What is GitHub Copilot?

An AI pair programmer that:

- Suggests code as you type
- Completes entire functions
- Adapts to your coding style
- Works within your IDE
- Learns from context in your files

. . .

**Availability:** Free for students, paid for others

## How Copilot Works

::: columns
::: {.column width="50%"}
**You write:**

```r
# Calculate mean water quality
# by district and year
```
:::

::: {.column width="50%"}
**Copilot suggests:**

```r
# Calculate mean water quality
# by district and year
water_summary <- water_data |>
  group_by(district, year) |>
  summarise(
    mean_quality = mean(quality,
                       na.rm = TRUE)
  )
```
:::
:::

## When to Use Copilot

::: {.incremental}
✅ **Good for:**

- Writing repetitive code patterns
- Boilerplate function structures
- Common data transformations
- Test case generation

⚠️ **Be cautious:**

- Always review suggestions
- May suggest outdated approaches
- Not always idiomatic R
- Security implications with sensitive data
:::

## Copilot in RStudio

::: {.callout-note}
## Setting up Copilot in RStudio

1. Install the Copilot extension (Tools → Global Options → Copilot)
2. Sign in with your GitHub account
3. Start typing - suggestions appear as grey text
4. Press Tab to accept, Esc to reject
:::

Learn more: [docs.github.com/copilot](https://docs.github.com/en/copilot)

# Approach 3: Agentic Work Mode {background-color="#4C326A"}

## What are Agentic AI Tools?

AI assistants that can:

- Execute complex multi-step tasks
- Read and write files autonomously
- Run code and review results
- Debug and iterate automatically
- Manage entire workflows

. . .

**Example:** Claude Code (formerly Cascade)

## Claude Code Overview

::: columns
::: {.column width="50%"}
**Capabilities**

- File system access
- Code execution
- Git operations
- Multi-file editing
- Autonomous debugging
- Context-aware decisions
:::

::: {.column width="50%"}
**Use Cases**

- Refactoring projects
- Building new features
- Debugging complex issues
- Setting up workflows
- Analyzing codebases
:::
:::

## {{< fa person-chalkboard >}} My Turn: Claude Code Demo {.center-align}

::: {style="margin-top: 30px"}
**Task:** Automated code analysis and improvement

I'll demonstrate:

1. Giving Claude Code a high-level task
2. Watching it read and analyze files
3. Seeing autonomous code improvements
4. Reviewing the changes
5. Understanding when to use this approach
:::

```{r}
#| echo: false
countdown(minutes = 10, seconds = 0)
```

## When to Use Agentic Tools

::: {.incremental}
**Best for:**

- Complex refactoring tasks
- Multi-file modifications
- Exploratory analysis of large codebases
- Automating repetitive workflows
- Learning unfamiliar code

**Consider carefully:**

- Requires trust in AI decisions
- Review all changes before committing
- More expensive than other approaches
- Needs clear task descriptions
:::

# Approach 4: R Packages for AI {background-color="#4C326A"}

## AI-Powered R Packages

Programmatic access to AI capabilities:

::: columns
::: {.column width="50%"}
**ellmer**

- New package from Posit
- Interface to multiple LLMs
- Structured data extraction
- Function calling support
- Cost-effective for batch tasks
:::

::: {.column width="50%"}
**Others to explore**

- gptstudio (RStudio addins)
- tidychatmodels (tidy interface)
- openai (direct API access)
- anthropic (Claude API)
:::
:::

## Why Use R Packages?

::: {.incremental}
1. **Reproducibility** - Code-based workflows you can rerun
2. **Automation** - Process many files/tasks programmatically
3. **Integration** - Seamless with existing R pipelines
4. **Control** - Fine-tune model parameters and prompts
5. **Cost tracking** - Monitor and optimize API usage
:::

## {{< fa person-chalkboard >}} My Turn: ellmer Demo {.center-align}

::: {style="margin-top: 30px"}
**Task:** Extract structured data from SFD PDF reports

I'll demonstrate:

1. Installing and setting up ellmer
2. Reading PDF documents
3. Creating extraction prompts
4. Extracting structured information
5. Processing results into data frames
:::

```{r}
#| echo: false
countdown(minutes = 15, seconds = 0)
```

## ellmer: Data Extraction Example

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "|1-2|4-9|11-13|15-17"
library(ellmer)
library(pdftools)

# Read PDF content
pdf_text <- pdftools::pdf_text(
  "3-2351-7-1448552001.pdf"
) |>
  paste(collapse = "\n")

# Create chat with extraction prompt
chat <- chat_claude() |>
  chat_append("Extract data availability from this SFD report...")

# Get structured response
result <- chat_perform(chat, data = pdf_text)

# Process into dataframe
extract_data_frame(result)
```

## API Costs Overview {.smaller}

Using AI programmatically has costs. Here's what to expect:

| Model | Input (per 1M tokens) | Output (per 1M tokens) | Typical PDF |
|-------|----------------------|------------------------|-------------|
| Claude Haiku | $0.25 | $1.25 | ~$0.01 |
| Claude Sonnet | $3.00 | $15.00 | ~$0.15 |
| GPT-4o mini | $0.15 | $0.60 | ~$0.01 |
| GPT-4o | $2.50 | $10.00 | ~$0.12 |

::: {.callout-tip}
## Cost Management

- Start with cheaper models (Haiku, mini)
- Process in batches
- Cache common queries
- Monitor usage with API dashboards
:::

## Setting Up API Access

::: columns
::: {.column width="50%"}
**Claude (Anthropic)**

1. Go to console.anthropic.com
2. Create account
3. Add payment method
4. Generate API key
5. Set `ANTHROPIC_API_KEY` in .Renviron
:::

::: {.column width="50%"}
**GPT (OpenAI)**

1. Go to platform.openai.com
2. Create account
3. Add payment method
4. Generate API key
5. Set `OPENAI_API_KEY` in .Renviron
:::
:::

. . .

**Security:** Never commit API keys to Git! Use `.Renviron` or password manager.

# Resources & Best Practices {background-color="#4C326A"}

## Key Resources

::: {.incremental}
1. **[Posit AI Newsletter](https://www.rstudio.com/tags/ai/)** - Latest AI tools for R
2. **[ellmer documentation](https://ellmer.tidyverse.org/)** - Package guides and examples
3. **[GitHub Copilot docs](https://docs.github.com/en/copilot)** - Setup and usage
4. **[Claude Code](https://claude.com/code)** - Agentic AI assistant
5. **[duck.ai](https://duck.ai)** - Free privacy-focused chatbot
:::

## Best Practices for AI-Assisted Coding

::: {.incremental}
1. **Always review** - Don't blindly trust AI output
2. **Understand the code** - Ask for explanations
3. **Start simple** - Iterate towards complexity
4. **Version control** - Commit before major AI changes
5. **Test thoroughly** - AI can introduce subtle bugs
6. **Learn continuously** - Use AI as a teaching tool
7. **Respect privacy** - Be careful with sensitive data
:::

## When to Use Which Approach?

| Approach | Best For | Time Investment |
|----------|----------|-----------------|
| **Chatbot** | Learning, quick tasks, brainstorming | Low |
| **Copilot** | Writing code, repetitive patterns | Medium |
| **Agentic** | Complex refactoring, large projects | High |
| **R Packages** | Batch processing, automation, APIs | Medium-High |

. . .

**Pro tip:** Combine approaches! Use chatbots to learn, Copilot while coding, packages for production.

## Ethical Considerations

::: {.incremental}
- **Attribution** - Understand licensing of AI-generated code
- **Privacy** - Don't share confidential data with AI services
- **Dependency** - Balance AI assistance with skill development
- **Bias** - AI models can reflect biases in training data
- **Verification** - You're responsible for code quality and correctness
:::

## Looking Forward

AI for coding is rapidly evolving:

::: {.incremental}
- Models are getting better and cheaper
- More R-specific tools emerging
- Integration becoming seamless
- Agentic capabilities expanding
- But fundamentals still matter!
:::

. . .

::: {.callout-important}
## Remember

AI is a powerful tool, but **you** are the programmer. Understanding R, data science principles, and problem-solving remains essential.
:::

# Questions? {background-color="#4C326A"}

## Next Steps

::: {style="margin-top: 50px"}
1. Complete the chatbot exercise if you haven't finished
2. Try ellmer for PDF extraction (see exercise repository)
3. Explore the resources shared today
4. Experiment with different AI approaches
5. Share your experiences in the Matrix chat
:::

## Course Completion

::: {.callout-note}
## Final Reminders

- **Capstone project due:** December 11, 2025
- **Quizzes 1-6:** Required for completion
- **Module 10:** Graduation event on December 18, 2025

You're almost there! 🎉
:::
