---
title: "{{< var md-10.title >}}"
subtitle: "{{< var course.long-title >}}"
author:
  - name: "{{< var author >}}"
  - name: "{{< var author2 >}}"
    affiliation: "{{< var institute >}}"
date-format: "MMM D, YYYY"
date: "2025-12-18"
format:
  revealjs:
    theme: slides.scss
    transition: fade
    slide-number: true
    logo: ../../img/OWD-logo-20.png
    chalkboard: true
footer: "[{{< fa link >}} {{< var course.site-short >}}]({{< var course.site >}})"
editor: source
execute:
  freeze: auto
editor_options:
  chunk_output_type: console
---

```{r}
#| include: false
library(countdown)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(knitr)
library(ggplot2)
library(gh)
library(lubridate)
library(here)
```

# Welcome {background-color="#4C326A"}

## {{< fa calendar >}} Agenda {.smallest .scrollable}

```{r}
#| echo: false
agenda <- read_csv(here::here("data/tbl-04-ds4owd-002-graduation.csv"))

agenda |>
    dplyr::mutate(
      time = format(start_time, "%H:%M"),
      # Create hyperlinked title if project_link exists
      title = ifelse(
        !is.na(project_link),
        paste0("[", title, "](", project_link, ")"),
        title
      )
    ) |>
    dplyr::select(time, duration, title, speaker) |>
    dplyr::mutate(
      duration = format(duration, "%M min"),
      speaker = ifelse(is.na(speaker), "", speaker)
    ) |>
    dplyr::rename_with(~stringr::str_to_title(.x), everything()) |>
    knitr::kable()
```

## Capstone project reviews

- Reviews completed end of January 2026
- Reviews are relatively minimal and support your needs (there is no pass/fail)
- [Please ask for specific advice if you would like help]{.highlight-yellow}
- Open an issue in your project repository to ask questions
- Tag instructors: @seawaR @larnsce

## Graduates Recognition

We will showcase course graduates on the openwashdata website:

- All completed projects will be featured
- Link to your report, GitHub profile, LinkedIn, ORCID
- Visit: [openwashdata.org/pages/academy/graduates](https://openwashdata.org/pages/academy/graduates/)

## Data Package Publication

For students with primary data in their capstone projects:

- We support data publication following open science workflows
- Create FAIR data packages with proper documentation
- Learn more: [github.com/openwashdata/fairenough](https://github.com/openwashdata/fairenough)

# Class Statistics {background-color="#4C326A"}

```{r}
#| echo: false
#| results: hide
# Source all auxiliary functions
source(here("src/check_mentions.R"))
```

```{r}
#| label: load-data
#| echo: false
#| results: hide
# Load from RDS (preferred - preserves data types)
if (file.exists(here("data/all_issues.rds"))) {
  all_issues <- readRDS(here("data/all_issues.rds"))
} else {
  stop("No data file found.")
}
```

```{r}
#| label: transform-data
#| echo: false
#| results: hide
# Extract assignment type and module number
instructors_users <- c("larnsce", "rainbow-train",
                       "massarin", "galacticasparagus",
                       "seawaR", "betadetective")

all_issues <- all_issues |>
  mutate(
    # Extract assignment type from repository name
    assignment = case_when(
      str_detect(repository, "md-\\d+") ~ str_extract(repository, "md-\\d+"),
      str_detect(repository, regex("samples", ignore_case = TRUE)) ~ "samples",
      str_detect(repository, regex("project", ignore_case = TRUE)) ~ "project",
      TRUE ~ NA_character_
    ),
    # Create module from assignment (keep as character for consistency)
    module = case_when(
      str_detect(assignment, "^md-\\d+$") ~ as.character(as.numeric(str_extract(assignment, "\\d+"))),
      assignment == "samples" ~ "3",
      assignment == "project" ~ "project",
      TRUE ~ NA_character_
    )
  ) |>
  filter(!created_by %in% instructors_users)
```

## Repositories with Issues by Module

```{r}
#| label: plot-by-module
#| echo: false
#| fig-height: 5
#| fig-width: 8
# Count unique repositories by module
module_counts <- all_issues |>
  filter(!is.na(module)) |>
  distinct(repository, module) |>
  count(module, name = "count") |>
  mutate(module = factor(module, levels = c(sort(setdiff(unique(module), "project")), "project")))

# Create bar chart
ggplot(module_counts, aes(x = module, y = count)) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = count), vjust = -0.5, size = 4) +
  labs(
    title = "Number of Repositories with Issues by Module",
    x = "Module",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12)
  )
```

## Student Retention Curve

```{r}
#| label: retention-curve
#| echo: false
#| fig-height: 6
#| fig-width: 10
# Calculate how many students reached each module
survival_data <- all_issues |>
  filter(!is.na(module)) |>
  mutate(module_label = ifelse(module == "project", "project", paste0("Module ", module))) |>
  select(created_by, module, module_label) |>
  distinct() |>
  # Exclude module 8
  filter(module != "8") |>
  group_by(module, module_label) |>
  summarize(n_students = n_distinct(created_by), .groups = "drop") |>
  arrange(module) |>
  mutate(
    retention_pct = (n_students / max(n_students)) * 100,
    dropout_pct = 100 - retention_pct
  )

# Create ordered factor for x-axis (equal spacing)
# Get numeric modules in order, then add project at end
numeric_modules <- survival_data |>
  filter(module != "project") |>
  arrange(as.numeric(module)) |>
  pull(module_label)

module_order <- c(numeric_modules, "project")

survival_data <- survival_data |>
  mutate(
    module_label = factor(module_label, levels = module_order),
    position = as.numeric(module_label)
  )

# Create line plot with equally spaced modules
ggplot(survival_data, aes(x = position, y = retention_pct)) +
  geom_line(color = "steelblue", linewidth = 1.5) +
  geom_point(size = 3, color = "steelblue") +
  geom_text(aes(label = paste0(round(retention_pct, 0), "%")),
            vjust = -1, size = 3.5) +
  geom_text(aes(label = paste0("n=", n_students)),
            vjust = 1.5, size = 3, color = "gray40") +
  scale_x_continuous(
    breaks = seq_along(module_order),
    labels = module_order
  ) +
  scale_y_continuous(limits = c(0, 105), breaks = seq(0, 100, 20)) +
  labs(
    title = "Student Retention Across Modules",
    x = "Module",
    y = "Retention Rate (%)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )
```

## Issues by Module and State

```{r}
#| label: plot-by-module-state
#| echo: false
#| fig-height: 5
#| fig-width: 8
# Count issues by module and state
module_state_counts <- all_issues |>
  filter(!is.na(module)) |>
  count(module, issue_state) |>
  mutate(module = factor(module, levels = c(sort(setdiff(unique(module), "project")), "project")))

# Create grouped bar chart
ggplot(module_state_counts, aes(x = module, y = n, fill = issue_state)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n), position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = c("open" = "#e74c3c", "closed" = "#27ae60")) +
  labs(
    title = "Issues by Module and State",
    x = "Module",
    y = "Count",
    fill = "Issue State"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12),
    legend.position = "top"
  )
```

## Distribution of Submissions

```{r}
#| label: plot-submission-distribution
#| echo: false
#| fig-height: 5
#| fig-width: 8
# Count submissions per student across all students (not just filtered ones)
all_submission_counts <- all_issues |>
  filter(!is.na(module)) |>
  select(created_by, module) |>
  distinct() |>
  count(created_by, name = "n_submissions")

# Count how many students have each submission count
submission_distribution <- all_submission_counts |>
  count(n_submissions, name = "n_students")

# Create bar chart
ggplot(submission_distribution, aes(x = factor(n_submissions), y = n_students)) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = n_students), vjust = -0.5, size = 4) +
  labs(
    title = "Distribution of Assignment Submissions",
    x = "Number of Assignments Submitted",
    y = "Number of Students"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```


# One last your turn {background-color="#4C326A"}

## Your Turn: Survey & Newsletter

::: {.incremental}

- Complete the [post-course survey: <https://forms.gle/cahqbLBoGt4eKu7K8> (5 minutes)
- Subscribe to the openwashdata newsletter: <https://buttondown.com/openwashdata> for future updates

:::

```{r}
countdown(6)
```

# Project Highlights {background-color="#4C326A"}

## Sílvia Paiva

Water inequalities across CPLP member states

<https://ds4owd-002.github.io/project-iamsilvia/>

## Mario Gavidia-Calderón

Air quality trends in the last decade

<https://ds4owd-002.github.io/project-quishqa/>

## Elisha Ochieng Okoth

Climate Variability in Kisumu County: An Analysis of Rainfall, Temperature, and Humidity (2021–2024)

<https://ds4owd-002.github.io/project-ElishaOkoth/>

## Ali Yousefi

Water Insecurity Experiences Among Rural Households in Chaharmahal and Bakhtiari Province, Iran

<https://ds4owd-002.github.io/project-yousefia601/>

## Jos van der Ent

Faecal sludge truck logistics analysis in Kampala, Uganda

<https://ds4owd-002.github.io/project-yozgoesdigital/>

## Farah Arbi

Water, Sanitation, and Hygiene (WASH) Indicators in North African Countries

<https://ds4owd-002.github.io/project-FarahArbi/>

## Mejbah Uddin Chowdhury

Evaluating the performance of fecal sludge treatment technologies in Rohingya refugee camps

<https://ds4owd-002.github.io/projectfstp-mejbahce1991/>

# Closing {background-color="#4C326A"}

Any last comments or questions?

# Thank you! {background-color="#4C326A"}

## Thanks!

Slides created via revealjs and Quarto: <https://quarto.org/docs/presentations/revealjs/>

Access slides as [PDF on GitHub]({{< var course.github-org >}}/website/raw/main/content/slides/lec-10-graduation.pdf)
